GravExplain

### 2019-12-19 paper/paper_main.tex
some rewording in the introduction

% general gw intro
In 2015 gravitational waves were observed for the first time from the merger of a binary black hole system. 
The observation, made by the Laser Interferometer Gravitational-wave Observatory~\citep[LIGO]{AdvancedLIGO:2015}, marked a breakthrough in modern astrophysics and provides a new means to observe the universe. 
Since then, the LIGO and Virgo~\cite{AdvancedVirgo:2015} observatories have made numerous detections of binary black hole~\cite{GW151226,GW170104,GW170814} and binary neutron star~\cite{GW170817,GW170817multi} mergers. 
With the increase in public interest in gravitational wave science, many gravitational wave research groups around the world have produced demonstrations and activities to explain this research to a general audience.
Activites range from online data analysis tutorials,~\cite{GWOSC:Online,LOSC:2015} hands-on demonstrations, phone apps,~\cite{LaserLabs:online,SciVR:online} and online games,~\cite{BlackHoleHunter:online} to exhibitions\han{add refs}, artistic interpretation, and musical performance \han{add refs}.

@@

% overview
In this article we describe how a Michelson interferometer can be used to demonstrate the search for continuous waves to a general audience. 
The techniques used here are very similar to those used by the real continuous wave searches. 
In section X we describe...... \han{add this in at the end}

>>>>

% general gw intro
In 2015 gravitational waves were observed for the first time from the merger two black holes in a binary system.~\cite{GW150914} 
The observation, made by the Laser Interferometer Gravitational-wave Observatory~\citep[LIGO]{AdvancedLIGO:2015}, marked a breakthrough in modern astrophysics and provides a new means to observe the universe. 
Since then, the LIGO and Virgo~\cite{AdvancedVirgo:2015} observatories have made numerous detections of binary black hole~\cite{GW151226,GW170104,GW170814} and binary neutron star~\cite{GW170817,GW170817multi} mergers. 
In recent years there has been an increased public interest in gravitaitonal-wave science. 
Many gravitational wave research groups around the world have produce demonstrations and activities to aid in explaining this topic to a general audience
Activites range from online data analysis tutorials,~\cite{GWOSC:online,LOSC:2015} hands-on demonstrations,\han{ref} phone apps,~\cite{LaserLabs:online,SciVR:online} and online games,~\cite{BlackHoleHunter:online} to exhibitions\han{add refs}, artistic interpretation, and musical performance \han{add refs}.

@@

% overview
In this article we describe how a Michelson interferometer can be used to demonstrate the search for continuous waves to a general audience. 
The techniques used are very similar to those used by researchers to search for continuous waves in LIGO and Virgo data. 
In section X we describe...... \han{add this in at the end}
